NOSQL\\ BEST PRACTICES

### 2018-03-27 pgconfus2018/presentation.tex
Highlight variable size columns
More slides and examples

@@

>>>>

        \begin{tikzpicture}[overlay,remember picture]
            \draw[line width=1mm, color=red, rounded corners]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(9.5,0.8)$) rectangle ($(\x1,\y2)+(12.0,-2.1)$);
        \end{tikzpicture}

@@

        \begin{tikzpicture}[overlay,remember picture]
            \draw[line width=1mm, color=red, rounded corners]
            let \p1=(start), \p2=(right) in ($(\x1,\y1)+(-0.3,0.8)$) rectangle ($(\x1,\y2)+(2.3,-2.1)$);
        \end{tikzpicture}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Document slide: in the DB or on the app?}

        \begin{itemize}[label={\MVRightarrow}]
            \item Amount of data passed from DB to application
            \item Performance hit in some cases\\ (multiple detoasting)
        \end{itemize}

        \includegraphics[width=0.75\textwidth,center]{select.png}

        \includegraphics[width=0.75\textwidth,center]{select_slice.png}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Indexing support}

        \begin{itemize}[label={\MVRightarrow}]
            \item GIN index (jsonb\_ops, jsonb\_path\_ops)
            \item Functional BTree index
            \item jsquery strategies for GIN
            \item Partial indexes WIP
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Jsonb array vs regular array}

        \begin{itemize}[label={\MVRightarrow}]
            \item Store elements of different type?\\
                    Not really a "single model" idea.
            \item Syntax is less natural (this may change)
            \item Updates are slower
            \item Arrays are 1-based, Jsonb 0-based
        \end{itemize}

    \end{center}
\end{frame}
\note {
    arrays are copied too, where exactly jsonb slower?
}

        \inputminted[
            fontsize=\normalsize,
        ]{sql}{sql/array_vs_jsonb.sql}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Some useful extensions}

        \begin{itemize}[label={\MVRightarrow}]
            \item jsquery
            \item postgres-json-schema
            \item is\_jsonb\_valid
            \item zson (jsonbc, custom compression methods WIP)
            \item jsonb\_explorer
        \end{itemize}

        \includegraphics[width=0.7\textwidth,center]{fuzzy.jpg}

        \vspace{-2cm}
        \tiny{\href{https://kickass-peanut.deviantart.com/}{@kickass-peanut}}

    \end{center}
\end{frame}
\note {
    "Types, please"
}

\fontsize{13pt}{14}\selectfont
\section{DBAs}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Limitations}

        \begin{itemize}[label={}]
            \item Size 256 MB
            \item Depth - max\_stack\_depth
            \item Stack depth is different for create \& update
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Statistics}

        \begin{itemize}[label={}]
            \item Size 256 MB
            \item Depth - max\_stack\_depth
            \item Stack depth is different for create \& update
        \end{itemize}
